---
title: "Best books of all times"
author: "Marian Nehrebecki, Aleksander Partyga, Magdalena Sobala"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: tactile
params:
  centries: 
    label: "Best books of all times"
    value: 4
    input: select
    min: 4
    max: 21
    step: 1
    sep: ""
---

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra) #common complex tables and manipulate table styles
library(dplyr)
library(ggtext)
library(ggplot2)
library(tidyverse)
library(tm)
library(wordcloud2)

knitr::opts_chunk$set(echo = FALSE, message = FALSE)
options(scipen = 999)
```



```{r, include=F, results=F}
books <- read.csv('data/book.csv')
books$titles<-str_trunc(books$titles,33)
head(books)
```

### Overview

(From the [Goodreads](https://www.goodreads.com)) Goodreads.com is the world’s largest site for readers and book recommendations. The mission of Goodreads  is to help people find and share books they love.

The users can rate their favourite books, create lists and share their opinion with their friends. The website also provides extensive information on books from all genres and centuries; it also provides the users with rankings, available by different parameters. The rankings that are of interst to us, are the rating by the century. Below you can find a short summary of each century's best books.

***


### A few things we can do on Goodreads

>* See what books our friends are reading. <br>
>* Track the books we' re reading, have read, and want to read.<br>
>* Check out our personalized book recommendations. The recommendation engine analyzes 20 billion data points to give suggestions tailored to our literary tastes. <br>
>* Find out if a book is a good fit for us from our community’s reviews.



```{r, include=F, results=F}
# Title of the best book
bb_title <- books$titles[books$scores==max(books$scores)]
```

***

## Summary of the best books of all time 

In total, we gathered available data from [Best Books By Century](https://www.goodreads.com/list/show/7), namely `r nrow(books)` unique book
titles along with their:

 * author
 * total score (which is based on number of votes and and how highly those voters ranked the book)
 * URL link
 * average rating
 * number of times rated


&nbsp;

## Visualisations: {.tabset}



### Books that were rated the most times 

```{r plot2, fig.align = 'center'}
sys.source("Plots.R", envir = knitr::knit_global())
plot2
``` 

The book that was rated the most times is  "**`r books$titles[books$times.rated==max(books$times.rated)]`**" written by **`r books$authors[books$times.rated==max(books$times.rated)]`** which was rated **`r max(books$times.rated)`** number of times. 

### Books with the highest total scores

```{r plot1, fig.align = 'center'}
sys.source("Plots.R", envir = knitr::knit_global())
plot1
```

The top rated book of all time is "**`r books$titles[books$scores==max(books$scores)]`**"  which was rated **`r books$times.rated[books$titles == bb_title]`** number of times and received an average rating of **`r books$average.rating[books$titles == bb_title]`**. 


### Most prolific authors

```{r plot3, fig.align = 'center'}
sys.source("Plots.R", envir = knitr::knit_global())
plot3
```


**`r unique(books$author[books$books_written == max(books$books_written)])`** is the author who has written the most books  (**`r max(books$books_written)`**) that were present in the Best Books by Century on Goodreads.