---
title: "RR project: Best Books By Century"
author: "Marian Nehrebecki, Aleksander Partyga, Magdalena Sobala"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  prettydoc::html_pretty:
    theme: cayman
params:
  centries: 
    label: "Best Books By Century"
    value: 4
    input: select
    min: 4
    max: 21
    step: 1
    sep: ""
---

```{r setup, include = FALSE}
library(tidyverse)
library(kableExtra) #common complex tables and manipulate table styles
library(dplyr)
library(ggtext)
library(ggplot2)
library(tidyverse)
library(tm)
library(wordcloud2)


knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_knit$set(base.dir = "Plots")

centries_data=paste0('data/centries_', params$centries, '.RData')
load(centries_data)

centries_data$average_rating = centries_data$`average rating`
centries_data$number=centries_data$`...1`
str(centries_data)
head(centries_data,1)
tail(centries_data,1)

```

# Best Books By Century `r params$centuries` summary in numbers



***

### Overview

(From the [Goodreads](https://www.goodreads.com)) Goodreads is the world’s largest site for readers and book recommendations. The mission of Goodreads  is to help people find and share books they love. Goodreads launched in January 2007. 

***


### A Few Things We Can Do On Goodreads

>* See what books our friends are reading. <br>
>* Track the books we' re reading, have read, and want to read.<br>
>* Check out our personalized book recommendations. The recommendation engine analyzes 20 billion data points to give suggestions tailored to our literary tastes. <br>
>* Find out if a book is a good fit for us from our community’s reviews.




### Centries `r params$centries` summary

**Century `r params$centries`** of *Goodreads* consisted of `r nrow(centries_data)` books that have been published by Author/Authors starting with **`r head(centries_data$authors, 1)`** and ending with **`r tail(centries_data$authors, 1)`**. The best book by `r params$centries` century: **`r centries_data[centries_data$votes==max(centries_data$votes), 'titles']`**  by `r centries_data[centries_data$votes==max(centries_data$votes), 'authors']`
gathered *`r round(max(centries_data$votes), 1)` votes*, *`r round(max(centries_data$scores), 1)` scores* and *`r round(max(centries_data$average_rating), 1)`* average rating. 

The above literature items can be found on the website:

>`r paste0("\"",centries_data[centries_data$votes==max(centries_data$votes), 'website'],"\"")`.


***






### Initial Analysis: {.tabset}

#### Score points of the books  by century `r params$centries`

It should be noted how the **scoring** changes for books by **century `r params$centries`** in Figure 1.



```{r rating_plot1, fig.align = 'center'}
centries_data %>% 
  ggplot(aes(x = as.numeric(number), y = scores)) +
  #geom_line(color = 'darkred', size = 1.2) +
  geom_bar(stat="identity", fill="darkred") +
  labs(title = 'Figure 1: Score points of the books  by century', x = 'Books number', 
       y = 'Score points of the books') +
  theme_minimal() + 
  theme(axis.title.y = element_markdown()) 
```
**Comments:**

* The maximum score points of the books by *century `r params$centries`* are equal `r round(max(centries_data$scores), 1)` 
for the book: **`r centries_data[centries_data$scores==max(centries_data$scores), 'titles']`**.

* The average score points of the books by *century `r params$centries`* are equal `r round(mean(centries_data$scores), 1)`.

* The minimum score points of the books by *century `r params$centries`* are equal `r round(min(centries_data$scores), 1)` 
for the book: **`r centries_data[centries_data$scores==min(centries_data$scores), 'titles']`**.



#### Votes of the books  by century `r params$centries`

It should be noted how the **votes** changes for books by **century `r params$centries`** in Figure 2.

```{r rating_plot2, fig.align = 'center'}
centries_data %>% 
  ggplot(aes(x = as.numeric(number), y = votes)) +
  #geom_line(color = 'darkred', size = 1.2) +
   geom_bar(stat="identity", fill="darkblue") +
  labs(title = 'Figure 2: Votes of the books  by century', x = 'Books number', 
       y = 'Votes of the books') +
  theme_minimal() + 
  theme(axis.title.y = element_markdown()) 
``` 
**Comments:**

* The maximum votes of the books by *century `r params$centries`* are equal `r round(max(centries_data$votes), 1)` 
for the book: **`r centries_data[centries_data$votes==max(centries_data$votes), 'titles']`**.

* The average votes of the books by *century `r params$centries`* are equal `r round(mean(centries_data$votes), 1)`.

* The minimum votes of the books by *century `r params$centries`* are equal `r round(min(centries_data$votes), 1)`.

#### Average rating of the books  by century `r params$centries`

It should be noted how the **average rating** changes for books by **century `r params$centries`** in Figure 3.



```{r rating_plot3, fig.align = 'center'}
centries_data %>% 
  ggplot(aes(x = as.numeric(number), y = average_rating)) +
  geom_line(color = 'darkgreen', size = 1.2) +
  
  labs(title = 'Figure 3: Average rating of the books  by century', x = 'Books number', 
       y = 'Average rating of the books') +
  theme_minimal() + 
  theme(axis.title.y = element_markdown()) 
``` 
**Comments:**

* The maximum average rating of the books by *century `r params$centries`* are equal `r round(max(centries_data$average_rating), 1)` 
for the book: **`r centries_data[centries_data$average_rating==max(centries_data$average_rating), 'titles']`**.

* The average rating of the books by *century `r params$centries`* are equal `r round(mean(centries_data$average_rating), 1)`.

* The minimum average rating of the books by *century `r params$centries`* are equal `r round(min(centries_data$average_rating), 1)` 
for the book: **`r centries_data[centries_data$average_rating==min(centries_data$average_rating), 'titles']`**.

***

Finally, the books with the above-average rating (see Table 1):

**Table 1.** The books with the above average rating 
```{r viewers-table1}

centries_data1 = centries_data[centries_data$average_rating > mean(centries_data$average_rating),]


centries_data %>% 
  filter(average_rating > mean(average_rating)) %>% 
  select(c(centries, titles, authors, website)) %>% 
  rename(`Century` = centries,
         `Title` = titles,
         `Author` = authors) %>% 

  kbl(row.names = FALSE) %>% 
  kable_styling(c('hover'), full_width = FALSE)
```

**Comments:**

* The total number of the books by *century `r params$centries`* are equal: **`r nrow(centries_data)`**.
* The number of books with the above average rating by *century `r params$centries`* are equal: **`r nrow(centries_data1)`**.




### References: 

https://www.goodreads.com
